Busting the Myth! - Reproducibility in ANS Performance

### 2019-09-26 paper.Rmd
updated base_format according to bookdown book. Removed word_document and commented out parts of YAML

---
title: "Busting the Myth! - Reproducibility in ANS Performance"
author:
- Enrico Spinielli
- Rainer Koelle
date: "`r format(Sys.time(), '%a %b %d %Y @  %X')`"
output:
  rticles::ieee_article:
    base_format: bookdown::pdf_book
    fig_caption: no
    includes:
      in_header: header.tex
      keep_tex: yes
      after_body: biographies.tex
    number_sections: yes
    toc: no
    with_dblfloatfix: no
    with_subfig: no
  html_document: default
  word_document:
    toc: no
bibliography: references.bib
# biblatex: true
color-links: yes
csl: ieee-transactions-on-aerospace-and-electronic-systems.csl
affiliation:
  # author-columnar: yes
  institution-columnar: true
  institution:
  - author:
    - email: enrico.spinielli@eurocontrol.int
      name: Enrico Spinielli
    - email: rainer.koelle@eurocontrol.int
      name: Rainer Koelle
    department: Performance Review Unit
    location: Brussels, Belgium
    name: EUROCONTROL
keywords:
- reproducibility
- ANS performance
- flight trajectory
- open data
- performance indicator
link-citations: yes
author-meta: Enrico Spinielli, Rainer Koelle
papersize: a4paper
abstract: |
  Air transportation is undergoing a fundamental transformation. On the political, strategic, and operational level work is directed to meet the future growth of air traffic.
  To meet this goal, operational concepts and technological enablers are deployed with the promises of distinct performance improvements. These improvements are typically widely marketed, however, the underlying evidence is not made available. From that respect Air Navigation System Performance suffers from the same credibility crisis seen in other industries. 
  This paper implements the reproducibility paradigm by providing data, code, and results openly to enable another researcher or analyst to reproduce - and potentially - improve or build on our work. This work is part of a wider thread to establish Open Data and Open Source based data analytical capabilities for Air Navigation System Performance in Europe.
  The implementation of the paradigm is demonstrated on the basis of the performance reference trajectory by replicating a classical performance measure, and then moving into investigating the application of trajectory based information for enhancing the current state of performance monitoring for the arrival phase. This paper applies the concept and approach as an use case analysis for 2 European airports with different strategies for sequencing arrival traffic (i.e. stack holding and point merge).
  The work reported demonstrates the feasibility of the approach and reflects a stepping stone in the roll-out of the performance reference trajectory within the European context. The work also builds the basis for novel developments on the basis of the implemented reproducibility workflow as this paper is accompanied by a webpage that supports the impartial evaluation of the work by providing the data, code, and how this reports had been produced.

title-meta: Busting the Myth! - Reproducibility in ANS Performance
---

>>>>

---
title: "Busting the Myth! - Reproducibility in ANS Performance"
author:
- Enrico Spinielli
- Rainer Koelle
date: "`r format(Sys.time(), '%a %b %d %Y @  %X')`"
output:
  bookdown::pdf_book:
    base_format: rticles::ieee_article
    fig_caption: no
    includes:
      in_header: header.tex
      keep_tex: yes
      after_body: biographies.tex
    number_sections: yes
    toc: no
    with_dblfloatfix: no
    with_subfig: no
  html_document: default
bibliography: references.bib
color-links: yes
csl: ieee-transactions-on-aerospace-and-electronic-systems.csl
affiliation:
  institution-columnar: true
  institution:
  - author:
    - email: enrico.spinielli@eurocontrol.int
      name: Enrico Spinielli
    - email: rainer.koelle@eurocontrol.int
      name: Rainer Koelle
    department: Performance Review Unit
    location: Brussels, Belgium
    name: EUROCONTROL
keywords:
- reproducibility
- ANS performance
- flight trajectory
- open data
- performance indicator
link-citations: yes
author-meta: Enrico Spinielli, Rainer Koelle
papersize: a4paper
abstract: "Air transportation is undergoing a fundamental transformation. On the political,
  strategic, and operational level work is directed to meet the future growth of air
  traffic.\nTo meet this goal, operational concepts and technological enablers are
  deployed with the promises of distinct performance improvements. These improvements
  are typically widely marketed, however, the underlying evidence is not made available.
  From that respect Air Navigation System Performance suffers from the same credibility
  crisis seen in other industries. \nThis paper implements the reproducibility paradigm
  by providing data, code, and results openly to enable another researcher or analyst
  to reproduce - and potentially - improve or build on our work. This work is part
  of a wider thread to establish Open Data and Open Source based data analytical capabilities
  for Air Navigation System Performance in Europe.\nThe implementation of the paradigm
  is demonstrated on the basis of the performance reference trajectory by replicating
  a classical performance measure, and then moving into investigating the application
  of trajectory based information for enhancing the current state of performance monitoring
  for the arrival phase. This paper applies the concept and approach as an use case
  analysis for 2 European airports with different strategies for sequencing arrival
  traffic (i.e. stack holding and point merge).\nThe work reported demonstrates the
  feasibility of the approach and reflects a stepping stone in the roll-out of the
  performance reference trajectory within the European context. The work also builds
  the basis for novel developments on the basis of the implemented reproducibility
  workflow as this paper is accompanied by a webpage that supports the impartial evaluation
  of the work by providing the data, code, and how this reports had been produced.\n"
title-meta: Busting the Myth! - Reproducibility in ANS Performance
---
